Enhancing Software Development with Artificial Intelligence

### 2023-07-11 Generative Software/proposal2.tex
2nd version (proposal under construction)

\title{Generative Software Development\\{\em\normalsize Research Offering}}
\author{prof.dr.ir.\ Stef Joosten\footnote{ORCID 0000-0001-8308-0189}}
\author{dr.\ Tim Steenvoorden\footnote{ORCID 0000-0002-8436-2054}}
\address{Open Universiteit Nederland, Heerlen, the Netherlands}

\begin{abstract}
    This paper summarizes the capability of the Open Universiteit in generative software development.
    We offer this enabling technology as a component of a larger effort that involves designing distributed information systems.
    Generative software development offers attractive benefits for correctness, security, and resilience.
    Also, it enables a product to be demonstrated live during its creation,
    hereby supporting agile software development methods.

    The ambition of this research is to contribute to solving the problem of large IT-projects.
    By generating fully functional information systems, we aim to reduce the effort and innovation risk of such projects.
    The direction of research goes toward more frequent deployments,
    which enables large projects to deliver incremental results in days rather than months.
    %every 2 or 3 weeks as it develops into an end product.
\end{abstract}

\begin{keyword}
    generative software, software engineering, security, prototyping, correctness, Ampersand, TopHat
\end{keyword}
\maketitle

>>>>

\title{Enhancing Software Development with Artificial Intelligence}
\author{prof.dr.ir.\ Stef Joosten\footnote{ORCID 0000-0001-8308-0189}}
\author{dr.\ Tim Steenvoorden\footnote{ORCID 0000-0002-8436-2054}}
\address{Open Universiteit Nederland, Heerlen, the Netherlands}

\begin{abstract}
    This proposal aims at supporting software engineers to develop software correctly and reliably by construction.
    The threshold of learning formal specification languages has kept scores of software engineers from using them in practice.
    Recent progress in Artificial Intelligence fuels the hope that AI might leverage the use of formal specification languages.
    This proposal aims at investigating how.

    The ambition of this research is to contribute to solving the problem of large IT-projects
    along the line of correctness and reliability.
\end{abstract}

\begin{keyword}
    generative software, AI enhanced software engineering, reliability by construction, prototyping, correctness by construction, Ampersand, TopHat
\end{keyword}
\maketitle
